Global code motion of congruent instructions

### 2017-04-18 paper.tex
some more rewording

\begin{verbatim}
// Return true if the merge-set of source node of a visited J-edge (incoming edge of
// lnode) is not the subset of the merge-set of lnode.
bool still_inconsistent(Node lnode, JEdges JE, Visited V, MergeSet MergeSet)
  for e in (all incoming edges to lnode)
    if (e is in JE && e in V)
      if (MergeSet(Source Node of e) is not a subset of MergeSet(lnode))
        return true
  return false

@@

// Construct merge-set of each node in Control-Flow-Graph G of a function.
void constructMergeSet(CFG G)
  B = Breadth First Order of G
  JE = JEdges of G
  DL = List of Path length (from root) of each node in G.
  do // Call until a fixed point is reached.
    Repeat = constructMergeSet_1(B, JE, DL)
  while (Repeat)
\end{verbatim}

@@

\section{Conclusions and Future Work}
\label{sec:future-work}

>>>>

\begin{verbatim}

// Return true if the merge-set of source node of a visited J-edge (incoming edge of
// lnode) is not the subset of the merge-set of lnode.
bool still_inconsistent(Node lnode, JEdges JE, Visited V, MergeSet MergeSet)
  for e in (all incoming edges to lnode)
    if (e is in JE && e in V)
      if (MergeSet(Source Node of e) is not a subset of MergeSet(lnode))
        return true
  return false

@@

// Construct merge-set of each node in Control-Flow-Graph G of a function.
void  constructMergeSet(CFG G) {
  B = Breadth First Order of G
  JE = JEdges of G
  DL = List of Path length (from root) of each node in G.

  do // Call until a fixed point is reached.
    Repeat = constructMergeSet_1(B, JE, DL)
  while (Repeat)
}
\end{verbatim}

@@

\section{Conclusion and Future Work}
\label{sec:future-work}
